Nested sampling with two objective functions

### 2015-11-01 Paper/ms.tex
New figure
sentence

\begin{algorithm}
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
\While{more iterations desired}
	\State Calculate the {\it corner count} (Equation~\ref{eqn:corner_count})
of each particle.
	\State Choose one of the particles which has corner count equal to the
minimum nonzero value. If all particles have a corner count of zero,
the algorithm terminates. Call the selected particle particle $K$.
	\State Choose one of the objective functions, and find $K$'s rank in terms
of that objective function.
\EndWhile
\end{algorithmic}
\end{algorithm}

Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.

@@

>>>>

\begin{algorithm}
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
\While{more iterations desired}
	\State Calculate the {\it corner count} (Equation~\ref{eqn:corner_count})
of each particle.
	\State Choose one of the particles which has corner count equal to the
minimum nonzero value. If all particles have a corner count of zero,
the algorithm terminates. Call the selected particle particle $K$.
	\State Choose one of the objective functions 
\EndWhile
\end{algorithmic}
\end{algorithm}

Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.
In Steps 2 and 3, we search for a particle with a low corner count, such as
one or two (so the fraction of the remaining prior mass to the lower left of
the chosen particle is approximately $1/N$ or $2/N$ respectively).

@@

\begin{figure}
\centering
\includegraphics[scale=0.75]{figures/output.png}
\caption{\label{fig:output}}
\end{figure}
